Viscous Transport in Eroding Porous Media

### 2019-09-06 docs/transport/erosion_transport.tex
working on results section

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Pore Throat Size}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
  \item Pore throat sizes affect many things such as first passage time,
  mixing, chemical reactions, heat conduction, biological activities
\end{itemize}

@@

In Figure~\ref{fig:Eroding20Transport}(a), we plot the tortuosity as a
function of the porosity from the initial porosity of $0.38$ until all
the bodies have eroded.  The tortuosity is computed with both the length
of the streamlines~\eqref{eqn:tortuosity1} (red marks) and using the
spatial average of the velocity on an Eulerian
grid~\eqref{eqn:tortuosity2} (blue marks).  The red square corresponds
to the porosity of the geometry in Figure~\ref{fig:Eroding20tort}(c).
The two tortuosity formulas give similar results, and any discrepancy
can be accounted for by slow regions of recirculation and quadrature
error induced by the integrals in the tortuosity definitions.  As the
bodies erode, this creates wide channels where streamlines undergo only
minor vertical deflections, and this explains why the tortuosity
eventually decreases with porosity.  We computed lines of best fit using
the porosity-tortuosity models~\eqref{eqn:tortuosityModels}, and the
power law model gave the smallest error.  The  black dashed line in
Figure~\ref{fig:Eroding20Transport}(a) is the line of best fit
\begin{align}
  \widehat{T}(\phi) = \phi^{-0.2064}
\end{align}
with a root-mean-square error of $5.90 \times 10^{-3}$.  The initial
increase in tortuosity occurs because in the absence of erosion (left
plot in Figure~\ref{fig:Eroding20vort}), many of the streamlines, such
as those initialized between bodies 15 \& 18, only perform minor
deflections to pass through the narrow regions, albeit, very slowly.
However, as erosion starts to open the channels, the streamlines deflect
into the fast regions, such as the region above body 11, and this
increases the amount of vertical deflection, and therefore the
tortuosity.

@@

Finally, following our previous work~\cite{qua-moo2018}, we analyze the
effect of erosion on the area fraction and the flow rate.  In
Figure~\ref{fig:Eroding20flowrate}(a), we plot the area fraction as a
function of normalized time.  Initially, 62\% of the geometry contains
eroding bodies corresponding to a porosity of $0.38$, and the area
fraction decreases to 0 as the bodies erode.  The trend of the area
fraction resembles our previous work~\cite{qua-moo2018} (Figure 10(a)),
but with a larger initial area fraction.  In
Figure~\ref{fig:Eroding20flowrate}(b), we plot the flow rate $U$
required to maintain a constant pressure drop across the channel.
Again, the trend of $U$ resembles that of our previous
work~\cite{qua-moo2018} (Figure 10(b)), except that the initial flow
rate is an order of magnitude smaller because of the larger initial area
fraction.  Starting around normalized time $0.2$,
Figure~\ref{fig:Eroding20flowrate}(b) is roughly linear which indicates
that the flow rate can be written as a power law.  Using a line of best
fit, the flow rate is approximately 
\begin{align} 
  U \approx \left(\frac{t}{t_f}\right)^{3.43},
\end{align}
which is the dashed line in Figure~\ref{fig:Eroding20flowrate}(b).

@@

We compute the tortuosity using the Eulerian
method~\eqref{eqn:tortuosity2}. In
Figure~\ref{fig:ErodingLow20Transport}(a), we plot the tortuosity with
respect to the porosity (blue) and the line of best fit (black) using
the power law 
\begin{align}
  \widehat{T}(\phi) = \phi^{-0.1669}.
\end{align}
This model outperformed the other three models in
equation~\eqref{eqn:tortuosityModels} that were proposed by Matyka et
al.~\cite{mat-kha-koz2008}.  The root-mean-squared error of the power
law is $1.13 \times 10^{-2}$.  As the bodies erode, the number of
streamlines that take a direct path through the geometry increases,
and this decreases the tortuosity.  However, there is also an increase
in the number of streamlines that increase their length since they
deflect their trajectory to move from a low porosity region (high
pressure) to a high porosity region (low pressure), and this decreases
the tortuosity. For this example, we see that the net effect is a
decrease in the tortuosity for all time.

In Figure~\ref{fig:ErodingLow20Transport}(b), we plot the temporal
evolution of the particle spreading $\sigma_\lambda$.  As in the last
example, we analyze the spreading at several different porosities and we
use the reinsertion algorithm described in Section~\ref{sec:dispersion}
to form sufficiently long trajectories to observe an asymptotic
dispersion rate.  For all the porosities, the dispersion is much closer
to ballistic when compared to the results in
Figure~\ref{fig:Eroding20Transport}.  However, there are still clear
transitions from ballistic dynamics at early times to asymptotic
super-diffusive dynamics.  In contrast to the lower porosity initial
condition (Section~\ref{sec:Eroding20}), at early times the erosion
results in a decrease in particle spreading. In particular, once erosion
has eroded the first 5\% of the bodies, the particle spreading
transitions from $\sigma_\lambda \sim t^{0.92}$ to $\sigma_\lambda \sim
t^{0.69}$.  To explain this behavior, note that the velocity is fairly
uniform, albeit small, at the initial condition (see
Figure~\ref{fig:ErodingLow20vort}).  Then as the geometry erodes, the
ratio of the fast and slow regions increases.  Since super-diffusive
dispersion results from a tracers spending times in a both slow and fast
regions, this results in an increase in the amount of super-dispersion.
\todo[inline]{Still need to work on this and explain how it contrasts
from the other 20 body example}
\todo[inline]{Need a reference for last sentence}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{100 eroding bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
As a final example, we consider 100 eroding bodies with an initial
porosity near 55\%.  Snapshots of the configurations and vorticity are
in Figure~\ref{fig:Eroding100vort}.  Again, by resolving near-contacts
with the Barycentric quadrature rule, a stable simulation is possible
with only $N_\iin = 256$ discretization points.  We use a time step size
of $\Delta t = 10^{-4}.$

\begin{figure}[H]
 \begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =0.9\linewidth]{./figs/100b_50}
\caption{}
%\caption{100 bodies and porosity = 55.54\% at t= 0.005}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =1.1\linewidth]{./figs/100b_100}
\caption{}
%\caption{99 bodies and porosity = 62.98\% at t= 0.01}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =0.9\linewidth]{./figs/100b_150}
\caption{}
%\caption{94 bodies and porosity = 72.22\% at t= 0.015}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =1.1\linewidth]{./figs/100b_200}
\caption{}
%\caption{82 bodies and porosity = 83.37\% at t= 0.02}
\end{subfigure}
\caption{\label{fig:Eroding100vort} Erosion of 100 bodies with the
  fixed-pressure-drop condition. The color is the vorticity of fluid. In
  this simulation, we use $N_\iin = 256$ discretization points on the
  body, $N_\out = 1024$ points on the outer wall, a time-step of
  $\Dt=10^{-4}$.  Because of the large number of bodies, erosion creates
  many channels connecting the inlet to the outlet.}
\end{figure}

To quantify the tortuosity, we compute the relative velocity
(Figure~\ref{fig:Eroding100tort}(a)) and the local tortuosity
(Figure~\ref{fig:Eroding100tort}(b)) of 1000 tracers placed immediately
to the left of the porous region at $x=-1$.  The porosity at this
instance in time is $62.98\%$ and the maximum velocity at $x=-1$ is
$3.90 \times 10^{-4}$. The initial velocity of the tracers is
qualitatively similar to the 20 body example
(Figure~\ref{fig:Eroding20tort}(a)), except with additional maximum and
minimums because of the additional bodies.  Compared to
Figure~\ref{fig:Eroding20tort}(b), the local tortuosity is much more
discontinuous.  These discontinuities can be explained by examining the
trajectories of tracers in Figure~\ref{fig:Eroding100tort}(c).  Here,
there are many instances of neighboring trajectories that are deflected
apart from one another as they tend to a stagnation point in the flow,
and this results in trajectories with significantly different lengths.
At this instance in time one the tracers travels 25.5\% farther than it
would have if the bodies had been absent, and the average tracer
travelled 12\% farther than it would have if the bodies were absent.
Therefore, at this instance in time, the tortuosity is $1.12$.

\begin{figure}[H]
\begin{subfigure}[b]{0.45\textwidth}
\begin{subfigure}[b]{\textwidth}
\includegraphics*[width =\linewidth]{./figs/velocity_loc100}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_local100}
\caption{}
\end{subfigure}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics[width = \textwidth]{./figs/100b_t100tracer}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding100tort} The tortuosity study in the fluid
with 100 bodies when the porosity is 62.98\%.  (a) The x-component
velocity u(-1, y) with respect to its maximum velocity $u_{max}=3.9021
\times 10^{-4}$ at equal spreading tracers on the cross section x = -1.
(b) The local tortuosity $\tau(y)$ on the cross section x = -1. (c) The
trajectories of 200 tracers released at $x = -1$ in the fluid with
multiple bodies.}
\end{figure}

The tortuosity at all porosities from the initial condition until all
the bodies have eroded is in Figure~\ref{fig:Eroding100Transport}(a).
The initial tortuosity is around $T=1.2$ and decays towards $T=1$.  The
tortuosities indicated by the blue dots are calculated using the
Eulerian approach~\eqref{eqn:tortuosity2}, while the red marks use the
Lagrangian approach~\eqref{eqn:tortuosity1}.  Again, the two methods
give comparable results indicating that any recirculation is small and
negligible.  As in the previous examples, the tortuosity depends on the
porosity through a power law model with a small root-mean-squared error
of $5.2 \times 10^{-3}$.  For this example, the logarithm tortuosity
model $\hat{T}(\phi) = 1 - p \ln(\phi)$ achieves a similar
root-mean-squared error.  The tortuosity has one interesting feature
near the end of the simulation where it suddenly increases.  This
behavior can be explained by ... \todo[inline]{S-H: Show me what is
going on here as we discussed.}

Next, we use the 1000 tracer trajectories to compute the second
(Figure~\ref{fig:Eroding100Transport}(b)) moments of the streamlines at
various porosities.  At high porosities, the first moment is similar to
the first-moment of trajectories in a empty channel (black dashed line).
At smaller porosities, the first moment is always linear, but larger
slopes indicate that the length of the trajectories are longer at lower
porosities \todo[inline]{Don't understand how this is the case}.  The
onset of anomalous dispersion is observed in
Figure~\ref{fig:Eroding100anomalous}. At early times, the particle
spreading is comparable to that of an open channel (dashed curve)
corresponding to the ballistic regime.  However, as the trajectories
traverse the geometry, a transition to a super-dispersive case,
especially at low porosities, is evident.  The dashed-dotted line
corresponds has a slope less than 1 indicating the long time behavior of
the trajectories
\begin{align*}
  \sigma_\lambda \sim t^{0.8715}.
\end{align*}

@@

Finally, using network models for flow in porous media~\cite{}, the
anomalous dispersion rate can be linked to channel widths between solid
bodies.  We construct a Delaunay triangulation with the centers of the
eroding bodies corresponding to the vertices of the triangles.  Then, if
the side of a triangle connects two vertices, we call the bodies
neighbors.  Then, for each pair of neighbors, we measure the distance
between the bodies.  Once a Delaunay triangulation is formed, it is used
for all subsequent time steps until a body completely disappears.  At
this point, a new Delaunay triangulation is formed. 
{\color{red}In Figure~\ref{fig:Eroding100gap_mean_var}, 
we record the gap distances between bodies neighbors and
calculate the mean and variance with respect to porosities. 
For the mean of gap distances, it is linearly increacing until $\phi = 85\%$ 
which means the eroding . 
For the variance of gap distances, it is almost a constant function until $\phi= 85\%$  }
\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height = 0.8\linewidth]{./figs/gap_mean}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height=0.8\linewidth]{./figs/gap_variance}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding100gap_mean_var}  The mean of gaps in (a) and 
the variancewith of gaps in (b) with respect to porosity $\phi$. 
Red stars are six selected porosities to have the details of  
the disturbutions of gaps and fitting curves of the disturbutions 
in Figure~\ref{fig:Eroding100gap_hist}.}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Pore Throat Size}
\label{sec:throats}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
  \item Pore throat sizes affect many things such as first passage time,
  mixing, chemical reactions, heat conduction, biological activities
\end{itemize}

@@

In Figure~\ref{fig:Eroding20Transport}(a), we plot the tortuosity as a
function of the porosity. The initial porosity is $\phi = 37.68\%$, and
the initial tortuosity is $1.16$.  The tortuosity is computed with both
the length of the streamlines~\eqref{eqn:tortuosity1} (red marks) and
using the spatial average of the velocity on an Eulerian
grid~\eqref{eqn:tortuosity2} (blue marks).  The red square corresponds
to the porosity of the geometry in Figure~\ref{fig:Eroding20tort}(c).
The two tortuosity formulas give similar results, and any discrepancy
can be accounted for by slow regions of recirculation and quadrature
error induced by the integrals in the tortuosity definitions.  As the
bodies erode, this creates wide channels where streamlines undergo only
minor vertical deflections, and this explains why the tortuosity
eventually decreases with porosity.  We computed lines of best fit using
the porosity-tortuosity models~\eqref{eqn:tortuosityModels}, and the
power law model gave the smallest error.  The  black dashed line in
Figure~\ref{fig:Eroding20Transport}(a) is the line of best fit
\begin{align}
  \widehat{T}(\phi) = \phi^{-0.2064}
\end{align}
with a root-mean-square error of $5.90 \times 10^{-3}$.  The initial
increase in tortuosity occurs because in the absence of erosion (left
plot in Figure~\ref{fig:Eroding20vort}), many of the streamlines, such
as those initialized between bodies 15 \& 18, only perform minor
deflections to pass through the narrow regions, albeit, very slowly.
However, as erosion starts to open the channels, the streamlines deflect
into the fast regions, such as the region above body 11, and this
increases the amount of vertical deflection, and therefore the
tortuosity.

@@

Finally, following our previous work~\cite{qua-moo2018}, we analyze the
effect of erosion on the area fraction and the flow rate.  In
Figure~\ref{fig:Eroding20flowrate}(a), we plot the area fraction as a
function of normalized time.  The general trend of the area fraction
resembles our previous work~\cite{qua-moo2018} (Figure 10(a)), but with
a larger initial area fraction.  In
Figure~\ref{fig:Eroding20flowrate}(b), we plot the flow rate $U$
required to maintain a constant pressure drop across the channel.
Again, the trend of $U$ resembles that of our previous
work~\cite{qua-moo2018} (Figure 10(b)), except that the initial flow
rate is an order of magnitude smaller because of the larger initial area
fraction.  Starting around normalized time $0.2$,
Figure~\ref{fig:Eroding20flowrate}(b) is roughly linear which indicates
that the flow rate can be written as a power law.  Using a line of best
fit, the flow rate is approximately 
\begin{align} 
  U \approx \left(\frac{t}{t_f}\right)^{3.43},
\end{align}
which is the dashed line in Figure~\ref{fig:Eroding20flowrate}(b).

@@

We compute the tortuosity using the Eulerian
method~\eqref{eqn:tortuosity2}.  The initial porosity is $30.67\%$ and
the initial tortuosity is $1.24$.  In
Figure~\ref{fig:ErodingLow20Transport}(a), we plot the tortuosity with
respect to the porosity (blue) and the line of best fit (black) using
the power law 
\begin{align}
  \widehat{T}(\phi) = \phi^{-0.1669}.
\end{align}
This model outperformed the other three models in
equation~\eqref{eqn:tortuosityModels} that were proposed by Matyka et
al.~\cite{mat-kha-koz2008}.  The root-mean-squared error of the power
law is $1.13 \times 10^{-2}$.  As the bodies erode, the number of
streamlines that take a direct path through the geometry increases,
and this decreases the tortuosity.  However, there is also an increase
in the number of streamlines that increase their length since they
deflect their trajectory to move from a low porosity region (high
pressure) to a high porosity region (low pressure), and this decreases
the tortuosity. For this example, we see that the net effect is a
decrease in the tortuosity for all time.

In Figure~\ref{fig:ErodingLow20Transport}(b), we plot the temporal
evolution of the particle spreading $\sigma_\lambda$.  As in the last
example, we analyze the spreading at several different porosities and we
use the reinsertion algorithm described in Section~\ref{sec:dispersion}
to form sufficiently long trajectories to observe an asymptotic
dispersion rate.  For all the porosities, the dispersion is much closer
to ballistic when compared to the results in
Figure~\ref{fig:Eroding20Transport}.  However, there are still clear
transitions from ballistic dynamics at early times to asymptotic
super-diffusive dynamics.  In contrast to the lower porosity initial
condition (Section~\ref{sec:Eroding20}), at early times the erosion
results in a decrease in particle spreading. In particular, once erosion
has eroded the first 5\% of the bodies, the particle spreading
transitions from $\sigma_\lambda \sim t^{0.92}$ to $\sigma_\lambda \sim
t^{0.69}$.  To explain this behavior, note that the velocity is fairly
uniform, albeit small, at the initial configuration (see
Figure~\ref{fig:ErodingLow20vort}).  Then as the geometry erodes, the
ratio of the fast and slow regions increases.  Since super-diffusive
dispersion results from a tracers spending times in a both slow and fast
regions, this results in an increase in the rate of super-dispersion.
\todo[inline]{Still need to work on this and explain how it contrasts
from the other 20 body example}
\todo[inline]{Need a reference for last sentence}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{100 eroding bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
As a final example, we consider 100 eroding bodies with an initial
porosity near 50\%.  Snapshots of the configurations and vorticity are in
Figure~\ref{fig:Eroding100vort}.  Again, by resolving near-contacts with
the Barycentric quadrature rule, a stable simulation is possible with
only $N_\iin = 256$ discretization points.  We use a time step size of
$\Delta t = 10^{-4}.$

\begin{figure}[H]
 \begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =0.9\linewidth]{./figs/100b_50}
\caption{100 bodies, $\phi = 55.54\%$}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =1.1\linewidth]{./figs/100b_100}
\caption{99 bodies, $\phi = 62.98\%$}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =0.9\linewidth]{./figs/100b_150}
\caption{94 bodies, $\phi = 72.22\%$}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =1.1\linewidth]{./figs/100b_200}
\caption{82 bodies, $\phi = 83.67\%$}
\end{subfigure}
\caption{\label{fig:Eroding100vort} Erosion of 100 bodies with the
  fixed-pressure-drop condition. The color is the vorticity of fluid. In
  this simulation, we use $N_\iin = 256$ discretization points on the
  body, $N_\out = 1024$ points on the outer wall, a time-step of
  $\Dt=10^{-4}$.  Because of the large number of bodies, erosion creates
  many channels connecting the inlet to the outlet.}
\end{figure}

To quantify the tortuosity, we compute the relative velocity
(Figure~\ref{fig:Eroding100tort}(a)) and the local tortuosity
(Figure~\ref{fig:Eroding100tort}(b)) of 1000 tracers placed immediately
to the left of the porous region at $x=-1$.  The porosity at this
time is $62.98\%$ and the maximum velocity at $x=-1$ is
$3.90 \times 10^{-4}$. The initial velocity of the tracers is
qualitatively similar to the 20 body example
(Figure~\ref{fig:Eroding20tort}(a)), except with additional maximum and
minimums because of the additional bodies.  Compared to
Figure~\ref{fig:Eroding20tort}(b), the local tortuosity is much more
discontinuous.  These discontinuities can be explained by examining the
trajectories of tracers in Figure~\ref{fig:Eroding100tort}(c).  Here,
there are many instances of neighboring trajectories that are deflected
apart from one another as they tend to a stagnation point in the flow,
and this results in trajectories with significantly different lengths.
At this time one the tracers travels 25.5\% farther than it would have
if the bodies had been absent, and the average tracer travelled 12\%
farther than it would have if the bodies were absent, so the tortuosity
is $1.12$.

\begin{figure}[H]
\begin{subfigure}[b]{0.45\textwidth}
\begin{subfigure}[b]{\textwidth}
\includegraphics*[width =\linewidth]{./figs/velocity_loc100}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_local100}
\caption{}
\end{subfigure}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics[width = \textwidth]{./figs/100b_t100tracer}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding100tort} The tortuosity study in the fluid
with 100 bodies when the porosity is 62.98\%.  (a) The x-component
velocity u(-1, y) with respect to its maximum velocity $u_{max}=3.90
\times 10^{-4}$ at equal spreading tracers on the cross section x = -1.
(b) The local tortuosity $\tau(y)$ on the cross section x = -1. (c) The
trajectories of 200 tracers released at $x = -1$ in the fluid with
multiple bodies.  The discontinuities in the local tortuosity correspond
to neighboring streamlines whose lengths are significantly different
because they pass opposite sides of an eroding body.}
\end{figure}

In Figure~\ref{fig:Eroding100Transport}(a), we plot the tortuosity as a
function of the porosity.  The initial geometry has a porosity of $\phi
= 50.09\%$ and the tortuosity is $T = 1.20$.  The tortuosity is computed
with both the length of the streamlines~\eqref{eqn:tortuosity1} (red
marks) and using the spatial average of the velocity on an Eulerian
grid~\eqref{eqn:tortuosity2} (blue marks).  The red square corresponds
to the porosity of the geometry in Figure~\ref{fig:Eroding100tort}(c).
Again, the two tortuosity formulas give similar results.  For this
geometry, the tortuosity decreases monotonically at almost all
porosities.  However, the tortuosity undergoes a sudden increase near
the end of the simulation.  The increase is caused by a single small
body near the middle of the channel being completely eroded.  While this
results in straighter streamlines, therefore reducing $\lambda$, the
horizontal flow, $u_x(y)$ increases since there is no longer a no-slip
boundary.  At the very late stages of erosion, we have observed that
when a single small body finishes eroding, this can result in a sudden
increase in the tortuosity.  We also computed the lines of best fit
using the porosity-tortuosity models~\eqref{eqn:tortuosityModels}.  The
black dashed line in Figure~\ref{fig:Eroding100Transport}(a) is the line
of best fit
\begin{align}
  \widehat{T}(\phi) = \phi^{-0.2459}
\end{align}
with a root-mean-square error of $5.50 \times 10^{-3}$.  We note a
slightly better root-mean-square error of $5.20 \times 10^{-3}$ is
possible with the model
\begin{align}
  \widehat{T}(\phi) = 1 - 0.2631 \ln(\phi).
\end{align}

\todo[inline]{do better job of explaining why diesperions does what it
does.  For this problem, there are lots more of small bodies rather than
a few big ones.  Therefore, after reinsertion, many of the bodies are
placed in a ballistic regime which means that anoamlous dispersion is no
longer observed.}
Next, we use the 1000 tracer trajectories to compute the second
(Figure~\ref{fig:Eroding100Transport}(b)) moments of the streamlines at
various porosities.  At high porosities, the first moment is similar to
the first-moment of trajectories in a empty channel (black dashed line).
Similar to the other previous examples, we initially observe ballistic
motion, and then super-diffusive dispersion.  However, similar to the
example in Figure~\ref{fig:ErodingLow20Transport}(b), the anomalous
dispersion rate is not growing with the porosity.  Therefore, it appears
that the dispersion rate in an eroding geometry depends not only the
porosity, but also the location and shape of the bodies.

@@

Finally, using network models for flow in porous media~\cite{}, the
anomalous dispersion rate can be linked to channel widths between solid
bodies.  As described in Section~\ref{sec:throats}, we use a Delaunay
triangulation to define neighboring eroding bodies, and we compute the
throat size by finding the closest distance between all neighboring
bodies.  Once all throat sizes are computed, we analyze their
distribution as a function of the porosity.  In
Figure~\ref{fig:Eroding100gap_hist}, we plot histograms of the throat
sizes at six porosities throughout the erosion process.

In Figure~\ref{fig:Eroding100gap_mean_var},
we plot the mean and variance of the throat sizes as a function of the
porosity.  While the mean steadily grows with the porosity, the variance
remains relatively flat for a wide range of porosities.

In Figure~\ref{fig:Eroding100gap_mean_var}, 
we record the gap distances between bodies neighbors and
calculate the mean and variance with respect to porosities. 
For the mean of gap distances, it is linearly increacing until $\phi = 85\%$ 
which means the eroding . 
For the variance of gap distances, it is almost a constant function until $\phi= 85\%$  
\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height = 0.8\linewidth]{./figs/gap_mean}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height=0.8\linewidth]{./figs/gap_variance}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding100gap_mean_var}  The mean of gaps in (a) and
the variance with of gaps in (b) with respect to porosity $\phi$.  Red
stars are six selected porosities to have the details of  the
distribution of gaps and fitting curves of the distributions in
Figure~\ref{fig:Eroding100gap_hist}.}
\end{figure}
